TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2019-06-10 paper/draft.tex
describe data-driven terminology in intro

In this work we build a data-driven model for M dwarf spectra with \thecannon\ (\citealt{Ness:2015}, \citealt{Ho:2017a}, \citealt{Casey:2016}, \citealt{Behmard2019}).
\thecannon\ is a pixel-by-pixel regression for spectral data given a training set of stars with reliable (assumed) accurate labels. The model can both predict a spectrum given labels, and also predict labels given a spectrum. Thus it is a generative model for stellar spectra that can be used for parameter inference.
%AWM: not an expert here, so I won't add anything, but this probably needs more information.

@@

\thecannon\ is a \emph{generative model} which parameterizes the flux at each pixel of a spectrum in terms of a set of stellar labels (a flexible number of parameters chosen by the user; described in more detail in Section \ref{sec:cannon}). The model in this sense is used to \emph{transfer} labels from spectra for which we know parameters to those which we do not. Hence this data-driven approach effectively circumvents the challenges of physically modeling the atmosphere of a star (and common issues associated such as incomplete line lists or opacities), provided that we have a subset of spectra in the dataset with known (and very accurately measured) \emph{reference labels} possibly measured from other data.

@@

\thecannon\ is a fully empirical model, which employs no use of line lists or radiative transfer models. Instead, \thecannon\ is a regression model which relies on two assumptions: first that sources with identical labels have near-identical flux at each pixel, and second that the expected flux at each pixel varies continuosly with change in label.

>>>>

In this work we build a data-driven model for M dwarf spectra with \thecannon\ \citep{Ness:2015,Casey:2016,Ho:2017a,Behmard2019}: a fully empirical model, which employs no use of line lists or radiative transfer models. 
\thecannon\ is instead a \emph{generative model} which parameterizes the flux at each pixel of a spectrum in terms of a set of stellar labels (a flexible number of parameters chosen by the user; described in more detail in Section \ref{sec:cannon}). The model in this sense is used to \emph{transfer} labels from spectra for which we know parameters to those which we do not. Hence this data-driven approach effectively circumvents the challenges of physically modeling the atmosphere of a star (and common issues associated such as incomplete line lists or opacities), provided that we have a subset of spectra in the dataset with known (and very accurately measured) \emph{reference labels} possibly measured from other data.

%AWM: not an expert here, so I won't add anything, but this probably needs more information.
%JB: I've swapped some sentences from section 2.2 and section 3, which explain the terminology. Do you think this paragraph adds enough clarity now without being too redundant with the following sections 2 & 3 describing The Cannon?

@@

\thecannon\ is a pixel-by-pixel regression for spectral data given a training set of stars with reliable (assumed) accurate labels. The model can both predict a spectrum given labels, and also predict labels given a spectrum. Thus it is a generative model for stellar spectra that can be used for parameter inference.

@@

\thecannon\ is a regression model which relies on two assumptions: first that sources with identical labels have near-identical flux at each wavelength pixel, and second that the expected flux at each pixel varies continuosly with change in label.
